---
layout: page
title: RStudio Trainer Program
subtitle: "Tidyverse: Predictive Model - Assessment"
author:
    name: xwMOOC
    url: https://www.facebook.com/groups/tidyverse/
    affiliation: Tidyverse Korea
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
editor_options: 
  chunk_output_type: console
---
 
``` {r, include=FALSE}
# source("tools/chunk-options.R")

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE,
                    comment="", digits = 3, tidy = FALSE, prompt = FALSE, fig.align = 'center')

```

# Multiple Choice Question {#assessment-multiple-choice}

Carefully look at `gapminder` dataset. We are going to build the world class predictive model? Which variable can be target variable?

1. country
1. continent  
1. year 
1. lifeExp      
1. pop gdpPercap

Hint: ["What Is the Most Important Thing in Life?"](https://www.pinchofattitude.com/what-is-the-most-important-thing-in-life/)

```{r gapminder-multiple-choice}
library(gapminder)

gapminder
```


# Parsons Problems {#assessment-parsons-problem}

- Use `gapminder` dataframe
- Group by `continent` and `country`, and then `nest()`
- Fit simple linear regression by each country through `mutate()`, `map()` pattern
- Extract $R^2$ values from list-columns
- Arrange country by $R^2$ values


```{r gapminder-parsons, eval=FALSE}
gapminder %>% 
  group_by(continent, ____) %>% 
  ____ %>% 
  mutate(model = map(____, ~lm(lifeExp ~ year, data=.))) %>% 
  mutate(model_glance = map(model, ____),
         rsquare = map_dbl(model_glance, ~.$r.squared)) %>% 
  arrange(_____))

```


