---
layout: page
title: RStudio Trainer Program
subtitle: "Tidyverse: Visualization - Lecture Note"
author:
    name: xwMOOC
    url: https://www.facebook.com/groups/tidyverse/
    affiliation: Tidyverse Korea
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
editor_options: 
  chunk_output_type: console
---
 
``` {r, include=FALSE}
# source("tools/chunk-options.R")

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE,
                    comment="", digits = 3, tidy = FALSE, prompt = FALSE, fig.align = 'center')

```

# Lecture Note {#RStudio-lecture-note}

- Static plot - `ggplot`
    - Interactive plot - `plotly`
    - Animation - `gganimate`
- Static plot - `ggplot`
    - Small Multiple - `facet_*`
    - Small Interactive Many - `trelliscopeJS`

# Static plot - `ggplot` {#viz-ggplot}

## Dataset - `gapminder` {#viz-ggplot-gapminder}

Identify the target variable from `gapminder` dataset.

```{r static-ggplot-data}
library(tidyverse)
library(gapminder)

gapminder %>% 
  DT::datatable()
```


## Visualize {#viz-ggplot-gapminder-static}

Select one country and visualize `lifeExp` trend over `year`.

```{r static-ggplot-data-viz}
gapminder %>% 
  filter(str_detect(country, "Korea, Rep")) %>% 
  ggplot(aes(x=year, y=lifeExp)) +
    geom_line() +
    geom_point()
```

Compare `lifeExp` with `gdpPercap` over `year`.

```{r static-ggplot-data-korea}
gapminder %>% 
  filter(str_detect(country, "Korea, Rep")) %>% 
  select(year, lifeExp, gdpPercap) %>% 
  gather(variable, value, -year) %>% 
  ggplot(aes(x=year, y=value)) +
    geom_line() +
    geom_point() +
    facet_wrap(~variable, scale="free")
```

Decorate through adding labels, title, and applying a theme.

```{r static-ggplot-data-korea-decorate}
library(extrafont)
loadfonts()

gapminder %>% 
  filter(str_detect(country, "Korea, Rep")) %>% 
  select(year, lifeExp, gdpPercap) %>% 
  gather(variable, value, -year) %>% 
  ggplot(aes(x=year, y=value)) +
    geom_line() +
    geom_point() +
    facet_wrap(~variable, scale="free") +
    labs(x="", y="", 
         title="GDP per capita and Life Expectancy over time",
         subtitle="Data from gapminder, Korea") +
    theme_bw(base_family = "NanumGothic")
```


# Interactive plot - `plotly` {#viz-interactive}

```{r interactive-ggplot}
life_p <- gapminder %>% 
    ggplot(aes(x=year, y=lifeExp, group=country)) +
    geom_line()  

library(plotly)  
ggplotly(life_p)
```

