---
layout: page
title: RStudio Trainer Program
subtitle: "Tidyverse: Visualization - Lecture Note"
author:
    name: xwMOOC
    url: https://www.facebook.com/groups/tidyverse/
    affiliation: Tidyverse Korea
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
editor_options: 
  chunk_output_type: console
---
 
``` {r, include=FALSE}
# source("tools/chunk-options.R")

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE,
                    comment="", digits = 3, tidy = FALSE, prompt = FALSE, fig.align = 'center')

```

# Lecture Note {#RStudio-lecture-note}

- Static plot - `ggplot`
    - Interactive plot - `plotly`
    - Animation - `gganimate`
- Static plot - `ggplot`
    - Small Multiple - `facet_*`
    - Small Interactive Many - `trelliscopeJS`

# Static plot - `ggplot` {#viz-ggplot}

## Dataset - `gapminder` {#viz-ggplot-gapminder}

Identify the target variable from `gapminder` dataset.

```{r static-ggplot-data}
library(tidyverse)
library(gapminder)

gapminder %>% 
  DT::datatable()
```


## Visualize {#viz-ggplot-gapminder-static}

Select one country and visualize `lifeExp` trend over `year`.

```{r static-ggplot-data-viz}
gapminder %>% 
  filter(str_detect(country, "Korea, Rep")) %>% 
  ggplot(aes(x=year, y=lifeExp)) +
    geom_line() +
    geom_point()
```

Compare `lifeExp` with `gdpPercap` over `year`.

```{r static-ggplot-data-korea}
gapminder %>% 
  filter(str_detect(country, "Korea, Rep")) %>% 
  select(year, lifeExp, gdpPercap) %>% 
  gather(variable, value, -year) %>% 
  ggplot(aes(x=year, y=value)) +
    geom_line() +
    geom_point() +
    facet_wrap(~variable, scale="free")
```

Decorate through adding labels, title, and applying a theme.

```{r static-ggplot-data-korea-decorate}
library(extrafont)
loadfonts()

gapminder %>% 
  filter(str_detect(country, "Korea, Rep")) %>% 
  select(year, lifeExp, gdpPercap) %>% 
  gather(variable, value, -year) %>% 
  ggplot(aes(x=year, y=value)) +
    geom_line() +
    geom_point() +
    facet_wrap(~variable, scale="free") +
    labs(x="", y="", 
         title="GDP per capita and Life Expectancy over time",
         subtitle="Data from gapminder, Korea") +
    theme_bw(base_family = "NanumGothic")
```


# Interactive plot - `plotly` {#viz-interactive}

```{r interactive-ggplot}
life_p <- gapminder %>% 
    ggplot(aes(x=year, y=lifeExp, group=country)) +
    geom_line()  

library(plotly)  
ggplotly(life_p)
```

## `tooltip` {#viz-interactive-tooltip}

```{r interactive-ggplot-tooltip}
tooltip_p <- gapminder %>% 
     ggplot(aes(x=year, y=lifeExp, 
                group=country, 
                text=paste0("Continent: ", continent, "\n", 
                            "Country: ", country, "\n", 
                            "Life Expectancy: ", lifeExp))) + 
     geom_line()
 
ggplotly(tooltip_p, tooltip = "text")
```


## Highlight {#viz-interactive-highlight}

```{r interactive-ggplot-highlight}
lifeExp_highlight <- highlight_key(gapminder, ~country)

highlight_p <- lifeExp_highlight %>% 
     ggplot(aes(x=year, y=lifeExp, 
                group=country, 
                text=paste0("Continent: ", continent, "\n", 
                            "Country: ", country, "\n", 
                            "Life Expectancy: ", lifeExp))) + 
     geom_line()
 
highlight_gg <- ggplotly(highlight_p, tooltip = "text")

highlight(highlight_gg, on = "plotly_click",
          selectize = TRUE,
          dynamic = TRUE,
          persistent = TRUE)
```

## Shared Link {#viz-interactive-sharedlink}

```{r interactive-ggplot-sharedlink}
life_cjk <- gapminder %>% 
    filter(country %in% c("China", "Japan", "Korea, Rep.")) %>% 
    ggplot(aes(x=year, y=lifeExp, group=country, 
             text=paste0("Continent: ", continent, "\n", 
                         "Country: ", country, "\n", 
                         "Life Expectancy: ", lifeExp))) + 
    geom_line() +
    geom_point() +
    facet_wrap(~country)

ggplotly(life_cjk, tooltip = "text")
```

## Shared Link - `htmlwidgets` {#viz-interactive-sharedlink-htmlwidgets}

```{r interactive-ggplot-sharedlink-hetero}
gapminder_cjk <- gapminder %>% 
  filter(country %in% c("China", "Japan", "Korea, Rep."))

gapminder_sd <- crosstalk::SharedData$new(gapminder_cjk)

## life expectancy by year
life_cjk <- gapminder_sd %>% 
  plot_ly(x = ~year, y= ~lifeExp, color=~country) %>% 
    add_markers() %>% 
    add_lines() %>% 
    highlight("plotly_selected", dynamic = TRUE)

gdp_cjk <- gapminder_sd %>% 
  plot_ly(x = ~gdpPercap, y= ~lifeExp) %>% 
    add_histogram2d() %>% 
    highlight("plotly_selected", dynamic = TRUE)

## bind two hetergeneous plots
crosstalk::bscols(life_cjk, gdp_cjk)
```

# Animation {#gapminder-animation}

```{r interactive-ggplot-animation}
life_g <- gapminder %>% 
  ggplot(aes(x=gdpPercap, y=lifeExp, group=country, color=country, 
             text=paste0("Continent: ", continent, "\n", 
                         "Country: ", country, "\n", 
                         "Life Expectancy: ", lifeExp))) + 
    geom_point(aes(frame=year), color="red") +
    geom_point(alpha=0.2) +
    facet_wrap(~continent, ncol=2) +
    scale_x_sqrt() +
    theme(legend.position = "none")

ggplotly(life_g, tooltip = "text")
```

## `gganimate` `transition_time()` {#gapminder-gganimate}

```{r gapminder-gganimate}
library(gganimate)
gapminder %>% 
  ggplot(aes(x=gdpPercap, y=lifeExp, group=country, color=country, 
             text=paste0("Continent: ", continent, "\n", 
                         "Country: ", country, "\n", 
                         "Life Expectancy: ", lifeExp))) + 
    geom_point(aes(size=gdpPercap)) +
    facet_wrap(~continent, ncol=2) +
    scale_x_sqrt() +
    theme(legend.position = "none") +
    transition_time(year) +
    labs(title = "Year: {frame_time}")
```

