---
layout: page
title: RStudio Trainer Program
subtitle: "Tidyverse: Visualization - Assessment"
author:
    name: xwMOOC
    url: https://www.facebook.com/groups/tidyverse/
    affiliation: Tidyverse Korea
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
editor_options: 
  chunk_output_type: console
---
 
``` {r, include=FALSE}
# source("tools/chunk-options.R")

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE,
                    comment="", digits = 3, tidy = FALSE, prompt = FALSE, fig.align = 'center')

```

# Multiple Choice Question {#viz-multiple-choice}

Why do we need visualization?

1. We can communicate visual artifacts with aspect ratio.
1. We can reduce cognitive load through visualization. 
1. Anscombe’s Quartet dataset provides rationals on why we always visualize a dataset.
1. Because we have three different visual systems(Base, ggplot, lattice) in R, we need a visualization.

Hint: [데이터 과학 - "시각화 (Visualization) 개요"](https://statkclee.github.io/viz/viz.html)


# Parsons Problems {#viz-parsons-problem}

<div class = "row">
  <div class = "col-md-4">
**Instruction**

- Import `trelliscopejs` library
- Filter out only "Americas" from continent and then group by `continent` and `country`, and then `nest()`
- Write `plot_ly` function named `lifeExp_plot` to visualize year and lifeExp
- Generate `trelliscopeJS` small **many** graphs using `map_plot()` and save list-column dataframe called `gapminder_plot_df`
- Visualize `gapminder_plot_df`

  </div>
  <div class = "col-md-8">
**Write Code**

```{r gapminder-viz, eval=FALSE}
library(____)

## list-column dataset
gapminder_nest <- gapminder %>% 
  filter(continent == "Americas") %>% 
  group_by(continent, country) %>% 
  ____()

## plotly graph function
lifeExp_plot <- function(df) {
    ____(df, x = ~year, y = ~lifeExp) %>% 
    add_markers() %>% 
    add_lines()
}

## Generate trelliscopeJS interactive graph 
gapminder_plot_df <- gapminder_nest %>% 
  mutate(panel = map_plot(data, ____))

trelliscope(____,
            name = "gapminder", nrow = 2, ncol = 3)

```

  </div>
</div>




